Adversarial State Aggregation

### 2020-01-19 minutia/paper/paper.tex
paper updated

>>>>

    \subsection{Aggregation}
    Find the best policy then find optimal number of buckets.
    Train the agent and retrieve the best policy then by running the agent with the best policy \textit{generate}
    samples.
    These collected samples are not based on a random policy but the best trained policy (baseline).
    Then we can test our hypothesis on the collected samples to see how discretization affect another trained agent.
    One way to measure the effect of discretization is average reward received by the trained agent.
